InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-06 paper.tex
Repo link
easily REMOVED
Co-authored-by: Max Buchholz <Max.Buchholz@gmx.de>
started extract

\section{Results + Discussion}
In the following section we take a look on the results of the aforementioned experiment.

@@

In fig. \ref{fig:gpt2} the text processors are plotted. The colors stay the same and the concept as well, where the left bar is using the radar evaluator and the right one the roberta base one. It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously. This is due to the typo processor since it alone also achieves great results. The radar evaluator only produces only black bars. 
Similar results can be seen in fig. \ref{fig:falcon} where radar just contains black bars and typo as well, as its combination with the roberta base evaluator achieves great results. The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.

@@

>>>>

\section{Results}
In the following section we take a look on the results of the aforementioned experiment.

@@

In fig. \ref{fig:gpt2} the text processors are plotted. The colors and the concept stay the same, the left bar is using the radar evaluator and the right one the roberta base one. It is visible that the double-whitespace processor solely has little effect whereas in combination with the typo processor the result rises enormously. This is due to the typo processor since it alone also achieves great results. The radar evaluator only produces black bars. 
Similar results can be seen in fig. \ref{fig:falcon} where radar and typo just contain black bars, as its combination with the roberta base evaluator achieves great results. The difference is that with the falcon generator and the roberta base evaluator in combination, some texts are detected as human made even before processing, which explains the red and grey parts.

@@

\section{Discussion}
